Global Optimization of an Analog Method by Means of Genetic Algorithms

### 2016-09-07 Moving temporal window - HESS/corrections/5 - Reply to referee 1.tex

\documentclass[]{letter}

\begin{document}

First of all, thank you for carefully reading the manuscript and for the constructive feedback.

Some referee comments are recalled in italics and followed by the authors’ responses. Others are addressed here, but without being recalled. The technical corrections or rephrasing are not discussed here, but will be performed.

\begin{itemize}
	\item Introduction: The structure will be changed and the description of the method moved into “Data and method”. Additional references will be added, and different variations will be presented, instead of relying on another papers to cover the literature review. The introduction will thus be rewritten.

	\item \textit{The issue discussed in the manuscript goes beyond this “fixed/moving” window issue. It more generally consider influence of the size of the data set (including the length of the archive) on the prediction skill. I am not aware of works that explored this issue but references to those, if any, and associated results have to be presented in the introduction.}

	The issue of the archive length will be better described, according to the relevant literature.

	\item \textit{The final objective of the work is to increase the prediction skill of the method. Other means are possible for this. They should be also mentioned.}

	We will mention other means to increase the prediction skill in the introduction.

	\item MTW strategy vs longer archive: We agree that the MTW might not be as performant as a 4 times longer archive, for the reasons provided. We indeed observed a gain in performance similar to doubling the archive. Your point on the transient climate is also interesting. We will add a discussion on these aspects in the paper.

	\item Number of analogs: we totally agree with the referee that when the choice of the predictors or the parameters are improved, leading to a better prediction, the optimal number of analog situations thus decreases. However, when the length of the archive increases, the optimal number of analogs increases too, for a better performance, up to a certain threshold. This has been demonstrated in the PhD of G. Bontron (2004, p. 227), and we can also see it in Fig.7 of Hamill et al. (2006). This increase in the number of analog situations results objectively in better performance skills in our case. The MTW enriches the pool of available situations, even though they are not fully independent. We will improve the clarity of this analysis. It is true though that the choice of predictors can be improved and auxiliary predictors are missing. The chosen methods are not the most recent ones, but are benchmarks as they have been used by several studies as a references. A note on that will be added.

	\item \textit{Explain both terms of the decomposition. Another well-known decomposition of the CRPSS is that of Herbasch. Please mention it also and clarify the advantage of that of Bontron. It is not clear at this stage.}

	We will remove the analysis of the sharpness and accuracy, as it brings unneeded complexity without being very instructive.

	\item \textit{Why using a non conventional notation for the CRPS score. Please use the classical one (CRPSS) or justify}

	It is the journal convention (“Multi-letter variables should be avoided. Instead use single-letter variables with subscript (e.g. ERMS instead of RMSE, or ET instead of ET).”) and we were asked to change the notation of the CRPS this way. We agree that is an unusual notation for this score… We are very open to change back these notations, if the editor says so.

	\item Resolution of the atmospheric reanalysis: it was shown by some studies that the resolution of the reanalysis dataset does not improve significantly the performance of the analogy of the atmospheric circulation. However, a full analysis of this aspect is out of the scope of this publication, and is a topic we are working on right now. Nevertheless, we can make the assumption that it does not alter the fact that we can find better analog situations at different hours of the day.

	\item Seasonal stratification: yes, we consider a seasonal stratification. It is mentioned in l. 36-39. This should be more clear after the change in the paper structure.

	\item \textit{You use the mean intensity of rainfall as a proxy of “dynamism of the atmospheric situation”. Another proxy could be the intensity of the variations within the geopotential fields (e.g. mean gradient value). Why did you not explore this? It would better fit to your “dynamism” concept.}

	Yes, that could be a possibility. However, even though the link between the dynamism and the precipitation amount is not direct, the interest in analyzing it this way is that it highlights improvements we are directly interested in: a better prediction of high precipitation amounts. This will be rephrased to focus more on the precipitation thresholds rather than the dynamism of the circulation pattern.

	\item Sharpness and accuracy: We will remove the analysis of the sharpness and accuracy, as mentioned previously.

	\item Figure 11: this figure is complex and not very instructive. It will be removed along with the sharpness and accuracy analysis.

	\item Tables: we agree that there are many tables. We will remove some unanalyzed data, such as the spatial windows in Tables 3, 4, 7, and 8 in order to group the remaining information. Tables 10 and 11 will also be removed along with the sharpness and accuracy analysis.

	\item The other unmentioned detailed issues will be fixed
\end{itemize}

\end{document}

### 2016-09-12 Genetic algorithms - MWR/template.tex
Reading and improving the paper.

\title{Global Optimization of an analog method by Means of Genetic Algorithms}

@@

\abstract{Analog methods are based on a statistical relationship between synoptic atmospheric variables (predictors) and local weather (predictand), which we aim at predicting. This relationship is expressed through many parameters that are often calibrated by means of a semi-automatic sequential procedure. This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and can get closer to a global optimum, by taking into account the parameters dependencies. Moreover, it can choose objectively parameters that were previously manually assessed, and can take into account new degrees of freedom.
These kind of optimization techniques need however to be tailored to the problem to solve. Multiple combinations of algorithms had to be assessed, and even new operators were developed, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods. These recommendations are the main outcome of this work. It opens new perspective for the improvement of analog methods, and their application to new regions or to new predictands.
}

@@

Analog methods (AMs) relies on the hypothesis that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}. The principle consists in sampling a certain number of past situations based on different atmospheric variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand). A common usage of AMs is for precipitation forecasting or downscaling \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Radanovics2013, Chardon2014, Dayon2015, Hamill2015b, BenDaoud2016}, but AMs, or equivalent, were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.

Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, at certain pressure levels and times of the day, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally the number of analog situations to keep.

AMs need to be adapted to every new region considered, because the leading meteorological influences may be location specific. Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself.

A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}. It determines some parameters of the method, for each consecutive analogy level (eg. the atmospheric circulation or moisture index), sequentially. It starts by a manual selection of the meteorologic variable (e.g. geopotential height, relative humidity, etc.), the pressure level (e.g. 500 hPa), the temporal window, and the initial analog number. Then, the spatial window on which the predictors are considered is optimized by an iterative growth of the domain, and the number of analogues is reassessed. A successive level of analogy can then be added and its spatial window optimized. Parameters of the preceding levels of analogy are not reassessed, except for the number of analogue situations to keep.

The sequential calibration procedure thus allows optimizing a limited number of parameters, but the selection of predictor variables, pressure levels and temporal windows had still to be made manually before optimizing the spatial windows and the number of analogs. Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy. Thus, optimizing the method with the sequential technique is laborious, as many combinations of predictors (variables, pressure levels, temporal windows) have to be assessed. Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another configuration if the parameters were calibrated together. Simultaneous calibration of all parameters has never been undertaken so far. Thus, due to the sequential approach, the risk of ending in a local optimum is high and can not be avoided. Indeed, during an AM calibration it has been found that the resulting parameters may vary with initial choices (such as the number of analogs).

When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?}''. And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of an AM and concludes that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions. \citet{BenDaoud2010}, when calibrating an AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''.

Another optimization strategy has been proposed by \citet{Junk2015}, that allows for an automatic optimization of weights applied to the different predictors when processing the analogy criteria (distance function). Their strategy consists in a brute-force assessment of all possible combinations. This approach is possible in their analog method, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to optimize. In the presently used analogue method (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.

In order to overcome these limitations, two optimization techniques were assessed. First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex algorithm. This technique did not provide satisfying results and failed at converging toward a unique solution. The parameter space of AMs can be very complex and is inappropriate for a linear optimization technique. The conclusion was that global optimization techniques were necessary in order to calibrate most AM variants, as it is the only way to optimize all parameters of all analogy levels simultaneously. In addition, it can overcome the systematic manual assessments of all pressure levels and temporal windows. Finally, it allows assessing new degrees of freedom, such as the use of differentiated spatial windows between the pressure levels. The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also work. If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations it very fast and lightweight.

This article is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize some AM variants. Indeed, GAs variants are numerous and always need to be tailored to the problem addressed. This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options. Such analyses are presented here by application to the upper Rh\^{o}ne catchment in Switzerland, and will result in recommendations for the use of GAs when applied to several AM implementations. The demonstration of the benefit brought by such an approach on a specific case study is the topic of another coming paper.

The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the basics of the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}). The comparative analyses of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.

@@

The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}). The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$. This region is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at allowing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}. Based on different climatological analyses, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).

The overall aim of the project is to implement a real-time precipitation and discharge forecasting in the catchment. An AM is used to provide real-time probabilistic forecasts of precipitation, based on NWP outputs. However, before being applied in the forecasting context, the AM must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.

@@

The AM relies on two types of data: predictors, that are atmospheric variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.

Working in the Perfect Prognosis framework, the meteorological archive from which the predictors are extracted is a reanalysis dataset. Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics \citep[MOS, see][]{Glahn1972} context, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.

@@

The predictand (which is to be predicted) is here the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network in the alpine upper Rh\^{o}ne catchment in Switzerland. The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}.

@@

AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}). Based on these analogue observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.

Predictors, for precipitation prediction, can be varied: e.g. geopotential heights at different pressure levels and on different temporal windows (time of observation), humidity variables, etc \citep[see][for a more detailed list]{BenDaoud2016}. The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (eg. atmospheric circulation, moisture variables, vertical motion, and air temperature).

@@

\begin{enumerate}
	\item Preselection: to cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive. Alternatively, the candidate dates can be selected based on similar air temperature \citep{BenDaoud2010}.

	\item First level of analogy: $n_{1}$ dates are selected out of the preselected $n_{0}$, by means of an analogy ranking. The first level of analogy is often based on the atmospheric circulation when it comes to precipitation prediction. The similarity of the atmospheric circulation of the target date with the candidate situations is thus assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g. 12~h and 24~h) by means of the S1 criteria \citep[Eq. (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. This criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.

@@

	The $n_{1}$ dates with the lowest values of S1 are considered as analogs, in terms of the general circulation, to the target day. The analog number, $n_{1}$, is a parameter to calibrate.

	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for similarities in other variables of interest, such as moisture variables. Therefore, the $n_{1}$ analogs are subsampled once again on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$. When the predictor is not a pressure field, the analogy criteria usually represents absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.

@@

	This process can be repeated, by subsampling a decreasing number of analogs, $n_{i}$, according to various meteorological variables.

	\item Probabilistic prediction of forecast: then, the (e.g. daily) observed precipitation amount of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.

@@

\begin{itemize}
	\item The selection of meteorologic variables, the predictors, that must contain large scale information having direct or indirect dependency with the local weather and the target predictand.
	\item The pressure level, or height, at which the predictor is considered.
	\item The spatial window is the domain on which the predictor is considered. The ideal size of this area is the one that maximizes useful information and minimizes noise.
	\item The temporal window is the hour in the day, or a set of different hours, at which the predictors are considered.
	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
	\item Eventual weights between the predictors \cite[e.g.][]{Horton2012a, Junk2015}
	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
\end{itemize}

In order to calibrate the method, the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000} has been often used to assess the AM performance \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. The mean CRPS of a prediction series of length $l$ can be written:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{l} \sum_{i=1}^{l} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
\end{equation}
where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.

@@

\begin{equation}
\label{eq:CRPSS}
CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect prediction (which implies $CRPS_{p}~=~0$). An increase in CRPSS means a better prediction.

>>>>

\title{Global Optimization of an Analog Method by Means of Genetic Algorithms}

@@

\abstract{Analog methods are based on a statistical relationship between synoptic meteorological variables (predictors) and local weather (predictand, which are to be predicted), which is defined by several parameters that are often calibrated by means of a semi-automatic sequential procedure. This calibration approach is fast, but has strong limitations: it is made of successive steps and thus cannot handle all parameters dependencies, and it cannot automatically optimize some parameters, such as the selection of the pressure levels and the temporal windows (hour(s) of the day) on which the predictors are compared.
In order to surpass these limitations, a global optimization technique was assessed, namely Genetic Algorithms, which can optimize jointly all parameters of the method and can get closer to a global optimum, by taking into account the parameters dependencies. Moreover, it can objectively calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom.
Genetic Algorithms need however to be tailored to the addressed problem. Multiple combinations of algorithms were assessed, and new ones were developed (e.g. the \textit{chromosome of adaptive search radius} which was found to be very robust), in order to make recommendations for the use of Genetic Algorithms to optimize several variants of analog methods. A global optimization approach opens new perspective for the improvement of analog methods, and their application to new regions or to new predictands.
}

@@

Analog methods (AMs) rely on the hypothesis that similar situations in terms of the atmospheric circulation are likely to lead to similar local weather \citep{Lorenz1956, Lorenz1969, Duband1970, Bontron2005}. They consist in sampling a certain number of past situations based on different synoptic-scale meteorological variables (predictors) in order to build a probabilistic prediction for a local weather variable of interest (predictand). A common usage of AMs is for operational precipitation forecasting \citep[eg.][]{Guilbaud1997, Bontron2005, Hamill2006, Bliefernicht2010, Marty2012, Horton2012, Hamill2015b, BenDaoud2016}, or more recently for precipitation downscaling in a climate perspective \citep[eg.][]{Radanovics2013, Chardon2014, Dayon2015}. However, AMs or equivalent were also used to predict temperature \citep{Radinovic1975, Woodcock1980, Kruizinga1983, DelleMonache2013, Caillouet2016}, wind \citep{Gordon1987, DelleMonache2013, DelleMonache2011, Vanvyve2015, Alessandrini2015, Junk2015, Junk2015c}, solar power \citep{Alessandrini2015a, Bessa2015}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}.

Even though the method is rather simple, it contains several parameters to optimize, such as the choice of the predictor variables, the pressure levels and temporal windows (hour(s) of the day) on which the predictors are compared, the spatial domains used for the comparison, as well as the analogy criteria (distance measure), and finally, the number of analog situations to retain.

AMs need to be adapted to every new region considered, because the leading meteorological influences may be location specific. Even the selection of the pressure levels and the temporal windows should be reconsidered, if not the predictor variable itself. Thus, before being applied in a forecasting or downscaling context, AMs must be calibrated for the given region, which is done here in the Perfect Prognosis framework \citep{Klein1963}, like the majority of AMs calibration procedures for precipitation prediction cited previously \cite[with the exception of][]{Hamill2006,Hamill2015b}.

A common approach to optimize the method is by means of a semi-automatic sequential calibration procedure, developed by \citet{Bontron2004}, also described in \citet{BenDaoud2016}, and extended by \citet{Radanovics2013}. It determines some parameters of the method, sequentially for each consecutive analogy level (eg. on the atmospheric circulation or on a moisture index). It starts by a manual selection of the meteorological variables (e.g. geopotential height, relative humidity, etc.), the pressure levels, the temporal windows, and the initial analog numbers. Then, the spatial window on which the predictors are compared is optimized by an iterative growth of the domain, and the number of analogs is finally reassessed. A successive level of analogy can then be added and its spatial window optimized. Parameters of the preceding levels of analogy are not reassessed, except for the number of analog situations to keep.

The sequential calibration procedure thus allows optimizing a limited number of parameters (spatial windows and analog numbers), but the selection of predictor variables, pressure levels and temporal windows have still to be made manually. Testing multiple combinations of these is very combinatorial and becomes quickly cumbersome, especially when considering multiple predictors within the same level of analogy. Thus, optimizing AMs by means of the sequential technique is laborious when little knowledge on the predictor-predictand relationship or the leading meteorological influences is available. Indeed, many combinations of parameters (predictor variables, pressure levels, temporal windows) have to be assessed. Moreover, proceeding to the optimization sequentially ignores potential dependencies between the parameters of the method, may they be within a single level of analogy or between them, which could lead to another configuration if the parameters were calibrated together. Thus, the risk of ending in a local optimum is high and can not be avoided.

When creating the sequential calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: ''\textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?}''. And later in his work: ''\textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution}''. \citet{Bliefernicht2010} has also faced the combinatorial issue of AMs parameters and concluded that one needs to be an expert to have a sense of their respective influence, sensitivity and nonlinear interactions. \citet{BenDaoud2010}, when calibrating an AM, also stated that ''\textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously}''. Simultaneous calibration of all parameters has never been undertaken so far.

Another optimization strategy has been proposed by \citet{Junk2015}, and allows for an automatic calibration of weights applied to the different predictors when processing the analogy criteria (distance function). Their strategy consists in a brute-force assessment of all possible combinations. This approach is possible in their implementation, as predictors are considered at a unique point (interpolated to the location of interest), at fixed hours, and at preselected pressure levels, leaving only the weights to be optimized. In the presently used AM (described in section \ref{sec:am}), the number of parameters to optimize makes it impossible to proceed to a brute-force strategy.

In order to overcome these limitations, two optimization techniques were assessed. First, \citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex algorithm. This technique did not provide satisfying results and failed at converging toward a unique solution. The parameter space of AMs can be very complex and is inappropriate for a linear optimization technique. Thus, global optimization techniques are likely to be necessary in order to calibrate most AM variants, as they can optimize all parameters of all analogy levels simultaneously. In addition, they can overcome the systematic manual assessments of all pressure levels and temporal windows. Finally, they allow testing new degrees of freedom in AMs. The relevance of Genetic Algorithms (GAs) is presented here, which does not exclude that other global optimization techniques could also work. If using GAs to optimize AMs is computationally intensive, once an AM is calibrated, its use in real-time operations or climate downscaling is very fast and lightweight.

This paper is not about discussing the details of the results of an optimization with GAs, but describing how GAs are to be used in order to successfully optimize several AMs. Indeed, GAs variants are numerous and always need to be tailored to the addressed problem. This requires intensive and systematic comparisons of operators and options in order to identify the key factors leading the optimization and the respective sensitivity of the options. Such analyzes are presented here and will result in recommendations for the use of GAs to optimize several AM implementations. The in-depth analysis of the benefit brought by such an approach on a specific case study is the topic of another coming paper.

The document starts by presenting the case study area and the data (section \ref{sec:case_study_data}), the considered AM variants (section \ref{sec:am}), and the assessed GAs options (section \ref{sec:gas}). The comparative analyzes of these options are presented in section \ref{sec:assessment}, which results in recommendations formulated in section \ref{sec:use} and conclusions in section \ref{sec:conclusions}.

@@

The study area is the alpine upper Rh\^{o}ne catchment in Switzerland (Fig.\ \ref{fig:map}). The altitude ranges from 372 to 4634~m.a.s.l.\ and the area is 5524~km$^{2}$.  Based on different climatological analyzes \cite[see][for the details]{Horton2012a}, the gauging stations in the catchment were clustered in 10~subregions (Fig.\ \ref{fig:map}).

The study area is the target of the MINERVE (Mod\'{e}lisation des Intemp\'{e}ries de Nature Extr\^{e}me sur les Rivi\`{e}res Valaisannes et de leurs Effets) project that aims at providing real-time flood management on the upper Rh\^{o}ne catchment \citep{GarciaHernandez2009b}. AMs are used to provide real-time probabilistic precipitation forecasts, based on NWP outputs.

@@

AMs rely on two types of data: predictors, that are meteorological variables describing the state of the atmosphere at a synoptic scale, and the predictand, which is the local weather time series one wants to predict.

When working in the Perfect Prognosis framework \citep{Klein1963}, the meteorological archive from which the predictors are extracted is usually a reanalysis dataset. Oppositely, other applications of AMs for wind forecasting are based on a Model Output Statistics context \citep[MOS, see][]{Glahn1972}, and thus use forecast archives or reforecast products \citep[e.g.][]{DelleMonache2013, DelleMonache2011, Alessandrini2015, Junk2015, Junk2015c}.

@@

The predictand (which is to be predicted) is here the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network in the catchment of interest. The time series from every available gauging station were averaged over subregions of approximately 500~km$^{2}$ \citep[see][for the details]{Horton2012a} in order to smooth local effects \citep{Obled2002, Marty2012}. The time series need to be split into a calibration and an independent validation periods.

@@

AMs are based on the principle that two similar synoptic situations may produce similar local effects \citep{Lorenz1956, Lorenz1969}. Thus, they consist in searching a certain number of past situations in a meteorological archive that present similar properties for chosen predictors, according to an analogy criteria, in order to extract the observed values of the local weather variable of interest from another archive (predictand time series, see section \ref{sec:case_study_data}.\ref{sec:data}). Based on these analog observations, the conditional empirical distribution considered as the probabilistic prediction for the target day (the day one wants to predict) is built.

Predictors for precipitation prediction, can be varied: e.g. geopotential height at different pressure levels and temporal windows, humidity variables, etc \citep[see][for a more detailed list of predictors]{BenDaoud2016}. The method often contains several levels of analogy, which are successive subsampling on predictors of different nature (eg. atmospheric circulation, moisture variables, vertical motion, and air temperature).

@@

\begin{enumerate}
	\item Preselection: to cope with seasonal effects, $n_{0}$ candidate dates are extracted from the archive within a period of four months centered around the target date, for every year of the archive. Alternatively, the candidate dates can be selected based on similar air temperature \citep[see][]{BenDaoud2016}.

	\item First level of analogy: $n_{1}$ dates are selected out of the preselected $n_{0}$, by means of an analogy ranking. The first level of analogy for precipitation prediction is often based on the atmospheric circulation. The similarity of the atmospheric circulation of the target date with the candidate situations is assessed on the geopotential height (at specific pressure levels, such as 500 and 1000~hPa, and over a certain spatial window, e.g. 12~h and 24~h) by means of the S1 criteria \citep[eq. (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a defined spatial window. The S1 criteria was found more relevant than Euclidean distances for pressure fields by different studies \citep{Wilson1980, Woodcock1980, Guilbaud1998, Bontron2004}.

@@

	The $n_{1}$ dates with the lowest values of S1 are considered as analog situations, in terms of the atmospheric circulation, to the target day. The analog number $n_{1}$ is a parameter to calibrate.

	\item Subsequent level(s) of analogy: beyond the similarity of airflows, one may look for analogies in other variables of interest, such as moisture variables. Therefore, the $n_{1}$ analogs are subsampled once again on the basis of another variable, in order to obtain a lower number of analog dates, $n_{2}$. When the predictor is not a pressure field, the analogy criteria usually represents absolute distances: Mean Absolute Error (MAE) and Root Mean Squared Error (RMSE), the latest being most often used.

@@

	This process can be repeated, by subsampling a decreasing number of analog dates, $n_{i}$, according to various meteorological variables.

	\item Probabilistic prediction: then, the daily observed precipitation amounts of the $n_{i}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.

@@

\begin{itemize}
	\item The selection of meteorological variables (predictors) that contain synoptic scale information having direct or indirect dependency with the target predictand.
	\item The pressure level, or height, at which the predictor is selected.
	\item The temporal window is the hour(s) of the day at which the predictors are considered.
	\item The spatial window is the domain on which predictors are compared. The ideal size of this area is the one that maximizes useful information and minimizes noise.
	\item The analogy criterion, needed to compare the variables on the chosen spatial and temporal windows, is a distance measure used for ranking observed situations according to their degree of similarity with the target situation.
	\item Eventual weights between the predictors \cite[e.g.][]{Horton2012a, Junk2015}
	\item The ideal number of analog situations, which is the best compromise in order to take into account local variability and to maximize useful synoptic information \citep{Bontron2004}.
\end{itemize}

In order to calibrate the method, the Continuous Ranked Probability Score \citep[CRPS,][]{Brown1974, Matheson1976, Hersbach2000} has often been used to assess AMs performances \citep[see, e.g.,][]{Bontron2004, Bontron2005, BenDaoud2008, Horton2012, Marty2012, Radanovics2013, Chardon2014, Junk2015, BenDaoud2016, Caillouet2016}. It allows evaluating the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analog situations, compared to the observed value $y^{0}$. The better the prediction, the smaller the score. The mean CRPS of a prediction series of length $l$ can be written:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{l} \sum_{i=1}^{l} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
\end{equation}
where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods.

@@

\begin{equation}
\label{eq:CRPSS}
CRPSS = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the score value for the reference. An increase in CRPSS means a better prediction.
